---
title: "Lab 01 - Hello R"
author: "Harrison Kane"
date: "12/26/2022"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)
1846 rows, 3 columns

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the circle dataset:

```{r plot-star}
circle <- datasaurus_dozen |>
    filter(dataset == "circle")
circle_data <- datasaurus_dozen |>
    filter(dataset == "circle")
ggplot(data=circle_data, mapping = aes(x=x, y=y)) + geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
circle_data |> summarize(r = cor(x,y))
```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
