---
title: "Lab 01 - Hello R"
author: "Harrison Kane"
date: "12/26/2022"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)
1846 rows, 3 columns

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen |>
    filter(dataset == "circle")
ggplot(data=circle_data, mapping = aes(x=x, y=y)) + geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data |> 
  summarize(r = cor(x,y))
```

### Exercise 4

First let's plot the data in the star dataset:

```{r plot_star}
star_data <- datasaurus_dozen |>
    filter(dataset == "star")
ggplot(data=star_data, mapping = aes(x=x, y=y)) + geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data |> 
  summarize(r = cor(x,y))
```

### Exercise 5

First let's plot all 13 datasets in the datasaurus_dozen:

```{r plot_datasaurus_dozen}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() + 
  facet_wrap(~ dataset, ncol = 3) + 
  theme(legend.position = "none")
```

Now calculate all the correlation coefficients:
``` {r cor_datasaurus_dozen}
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y)) 
```

All of the datasets in the datasaurus_dozen have a very slightly negative correlation between x and y (roughly r = -0.06 for all 13 datasets), indicating little relationship between the variables.