---
title: "Lab 01 - Hello R"
author: "Harrison Kane"
date: "12/26/2022"
output:
  pdf_document: default
  html_document: default
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows, 3 columns

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen |>
    filter(dataset == "circle")
ggplot(data=circle_data, mapping = aes(x=x, y=y)) + geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data |> 
  summarize(r = cor(x,y))
```

### Exercise 4

First let's plot the data in the star dataset:

```{r plot_star}
star_data <- datasaurus_dozen |>
    filter(dataset == "star")
ggplot(data=star_data, mapping = aes(x=x, y=y)) + geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data |> 
  summarize(r = cor(x,y))
```

### Exercise 5

First let's plot all 13 datasets in the datasaurus_dozen:

```{r plot_datasaurus_dozen}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() + 
  facet_wrap(~ dataset, ncol = 3) + 
  theme(legend.position = "none")
```

Now calculate all the correlation coefficients:
``` {r cor_datasaurus_dozen}
datasaurus_dozen |>
  group_by(dataset) |>
  summarize(r = cor(x, y)) 
```

All of the datasets in the datasaurus_dozen have a very slightly negative correlation between x and y (roughly r = -0.06 for all 13 datasets), indicating little relationship between the variables.